\documentclass[10pt,notitlepage,twoside,a4paper]{scrartcl}
%
\include{headers}
%

\date{2010-11-25}

\begin{document}
 \include{title}
 \tableofcontents
 \newpage
 \section{Introduction}
\par The LumiCal Simulation [{\bfseries LuCaS}] package is easy to use {\bf GEANT4} based application devoted for simulation of LumiCal (the luminosity monitor for ILD). Entire FCAL ( Forward Calorimetry ) detectors of ILD ( LumiCal, LHCAL, BCAL beam pipe and mask ) are build, but only LumiCal is set to be sensitive detector ({\it i.e.} hits are stored in the output file).
\newpage

 \section{Installation}\label{instal}
The LuCaS package need $Geant4$ and ROOT packages to be installed on the system.
After unpacking tarball, move to the directory LUMICAL
\begin{itemize}
 \item $>$cd LUMICAL
\end{itemize}

then inspect file setup.csh ( setup.sh if you are working with bash )
and make appropriate to your environment changes. Particulary specify location where Geant4 and ROOT
packgages are installed. Execute:
\begin{itemize}
\item $>$ source  setup.csh ( or if you are running bash  $>$. setup.sh )
\item $>$ gmake
\end{itemize}

this ( if succesfull ) will create {\bfseries{./bin/$<$OS-SYSTEM$>$}} directory where the {\bfseries{Lucas}} executable will be placed.
Now you are ready to run the program. For convinience you may want add the path to {\bfseries{Lucas}} location in to your {\bfseries PATH} environment variable.
\newpage
 \section{Using LuCaS}\label{use}
If everything went O.K. now you can start the Lucas with default confinguration in the interactive mode executing command :\\
{\bf {$>$ Lucas -i }}\\
One may want to inspect {\bf {./geant4-macros}} directory to see available visualisation macros.
 \subsection{Command line parameters}\label{params}
Full list of available command line parametrs can obtained with command:\\
{\bf {$> $Lucas -h}}\\
this will print on your screen :\\
\begin{verbatim}
Usage:          Lucas [options]


-h              print this help message and exit
-b              batch mode
-i              interactive mode (default)

-m <filename>   specifies a macro file to be executed before running
                (default none)

-o <filename>   specifies file name for ROOT output.No default
-M <mode>       specifies ROOT file opening mode ( default is NEW
                to avoid accidental file overwriting
                Possible values are RECREATE/UPDATE
-A              accumulate events from entire Run are to be
                written in one event ( suitable only for beam background data )

-c <double>     specifies the Geant 4 production range cut in mm 
                (default is 0.005 mm)
-x <double>     specifies the Beam Crossing Angle in mrad
                (default is 0 [mrad])
-s <filename>   specifies name of the file with geometry setup
-P <int>        specifies printout level ( default is 0= minimum
                                                      3= debug printout
\end{verbatim}

\newpage
 \subsection{Steering file parameters}\label{steer}

\begin{table}[http]\label{lcalpars}
\begin{center}
\begin{tabular}{lrl}
\hline
 Parameter name & Default value &  Description \\
\hline
\bf{Lcal\_z\_end}       & 2635.0 mm & defines distance of LumiCal from IP\\
\bf{Lcal\_inner\_radius}&   76.0 mm & absorber inner radius \\
\bf{Lcal\_outer\_radius}& 197.2 mm  & absorber outer radius\\
\bf{Lcal\_SensRadMin}   &  80.0 mm  & silicon sensor inner radius\\
\bf{Lcal\_SensRadMax}   & 195.2 mm  & silicon sensor outer radius\\
\bf{Lcal\_n\_layers}    &       30  & number of detector planes\\
\bf{Lcal\_n\_tiles}     &       12  & number of in one sensor plane\\
\bf{Lcal\_n\_sectors}   &       48  & number of azimuthal divisions\\
\bf{Lcal\_n\_rings}     &       64  & number of radial divisions\\
\bf{Lcal\_virtual\_cells}& 1 & virtual cells are used instead building physical one \\
& 0 & physical cells will be used\\
\end{tabular}
\caption{Full list of Lucas geometry control parameters.}
\end{center}
\end{table}
 \subsection{Accessing output tree}\label{treeacces}

\end{document}
